---
title: "Fiscal exemptions for high-skilled foreign workers"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Several tax exemptions have been set up in order to attract high-skilled workers. These exemptions are often temporary measures, subject to income levels and eligibility requirements. Specific jobs are sometimes targeted, especially knowledge-based activities (profesors, researchers...). 

There has been a clear acceleration of this type of measurement in recent years. Countries that have been rather reluctant to implement them so far (France, for example) have been forced to do so. 

# France

2018 | 7 | 23 Last compiled: `r Sys.Date()`

## The regime of impatriate workers 

### Exemptions

The impatriate regime provides for income tax exemptions for persons domiciled for tax purposes outside France during the 5 calendar years preceding their employment in a company established in France (intra-group mobility or external recruitment). Exemptions are provided for in [Article 155B of the CGI](https://www.legifrance.gouv.fr/codes/article_lc/LEGIARTI000037985788/)

There are also exemptions for expenses. There are three categories:

- The operating costs falling under [Article 81 of the CGI](https://www.legifrance.gouv.fr/codes/article_lc/LEGIARTI000038836748/2019-10-01)
- Specific allowances for impatriates (additional cost of housing and tax equalization)
- Other specific indemnities (impatriation bonus seen below, personal expenses, home improvement and household appliancesd expenses, automobile purchase expenses). 

Other exemptions are possible:

- The impatriation bonus, which must be explicitly mentioned by the employer and whose amount withdrawn from the total remuneration must result in a reference remuneration (comparable to that of a tax resident in France with the same skills and the same job). 

- The share of the remuneration for activities carried out abroad

- 50% of income from movable capital from foreign sources (if coming from countries that have a convention with France in the context of the fight against tax fraud).

- 50% of certain intellectual or industrial property income from foreign sources (under the same conditions as before)

- 50% of gains on the disposal of securities and employee rights from foreign sources 

In addition, the employee can also deduct social security contributions paid abroad :

- Paid to statutory pension schemes of the Social Security in their home country (8 years)
- Paid into supplementary pension schemes (up to 5% of the URSSAF ceiling)
- Paid into professional supplementary pension schemes (8% of annual remuneration up to 8 times the URSSAF ceiling). 


### Limitations

There is a cap on certain exemptions with a choice :

- An overall cap at 50% of the total remuneration: impatriation bonus + part of the remuneration for activities carried out abroad
- A cap on compensation for activities carried out abroad at 20% of total compensation

### Duration 

The exemptions last until the end of the eighth calendar year since the 2017 Finance Act (fifth year for the previous period). An employee can therefore benefit from them for 9 years if he takes up his duties on January 1st of the year. The plan ends automatically if the employee leaves the company before the end of the term but not if he changes functions. 


## HQ and logistics center employees

The terms and conditions for the exemption of HQ and logistics center employees are provided for in the [Bulletin officiel des impôts](https://bofip.impots.gouv.fr/bofip/5665-PGP.html/identifiant=BOI-RSA-GEO-50-20170621). 

Both allowances are deductible from income tax :

- Additional cost of housing in relation to the country of origin
- Tax equalization

Additional costs must be justified.

Conditions:

- the employee must not have been domiciled for tax purposes in France during the five calendar years prior to his or her arrival in France;

- and the headquarters or logistics center must opt to subject these two allowances to a tax calculated at the standard corporate tax rate and related contributions in lieu of income tax on behalf of the employee.

The employee may also benefit from the reimbursement of his professional expenses in the same manner as impatriates, as provided for in Article 81 of the CGI.

## Employees and managers of International Chamber of Commerce

Employees and managers called from abroad to take up employment with the International Chamber of Commerce in France after 2011 are not subject to income tax on the salaries and wages paid to them in this capacity for five years, provided they have not been tax domiciled in France for the last five years.

They cannot benefit from article 155B of the French General Tax Code. 

# Belgium 

2018 | 7 | 23 Last compiled: `r Sys.Date()`

The special Belgian tax regime is governed by the [Circulaire n° Ci.RH.624/325.294 de 1983](https://lex.be/fr/doc/be/fisconet-fiscal-discipline/circulaire-n-cirh624325294-dd-08081983-8-aout-1983-befp_19830808558b4842_fr). It applies to executives of foreign nationality, with positions requiring specific skills and responsibilities. In addition, they must be in one of the following three cases:

- Being temporarily seconded by foreign companies
- Being temporarily seconded by a large international group
- Being recruited by a Belgian company, subsidiary of a foreign company or member of an international group
- Being a foreign director holding functions in this type of company
- Being a non-managerial worker but specialized in a field where recruitment in Belgium is difficult.
- Being a researcher or a scientist

The temporary nature of the activity must be proven, in particular by :

- the stay of the spouse or children abroad;
- the provision of a dwelling abroad;
- the fact that the children continue to be educated abroad;
- possession of real or personal property abroad;
- the existence of a life insurance policy outside Canada;
- a continued participation in a group insurance contract or other savings or pension plan outside Canada;
- the insertion of a "diplomatic clause" in the lease agreement.

Foreign executives residing for tax purposes in Belgium can deduct from their taxable income :

* expenses reimbursable by the employer and which constitute additional expenses related to the installation in Belgium, including :
    * non-repetitive expenses and charges resulting from the installation in Belgium
    * repetitive expenses and charges: tax equalization, cost of living variance, etc.

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the sam place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation =1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag), from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You learn all of these things and more can be customized in each R code block.

# The big idea

Use this lab journal to record what you do in R. This way I will be able to see what you are doing and help you along the way. You will also be creating a repository of all the things you do. You can make posts about everything. Learning specific things in R (project unrelated), and doing things for the project that we will discuss at the beginning of the Fall semester. You can get started now by fiddling around with googling things, and trying stuff out in R. I've placed some helpful starting links in the links page on this website

# What can you do right now by yourself?

It's hard to learn programming when you don't have specific problems that you are trying to solve. Everything just seems abstract.

I wrote an [introductory programming book that introduces R](https://crumplab.github.io/programmingforpsych/), and gives some [concrete problems for you to solve](https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html). 

To get the hang of journaling and solving the problems to learn programming, my suggestion is that you use this .Rmd file to solve the problems. It would look like this:

# Problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+2
2*5
5/3
(1+6+4)/5

```

# Problem 2

Put numbers into variables, do simple math on the variables

```{r}
a<-1
b<-2
a+b

d<-c(1,2,3)
e<-c(5,6,7)
d+e
d*e
d/e

```

# Problem 3

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
# for loop solution
# i becomes the number 1 to 100 at each step of the loop


a <- length(100) # make empty variable, set length to 100
for (i in 1:100){
  a[i] <-i #assigns the number in i, to the ith index of a
}

print(a)

# for loop solution #2

a<-c() #create empty variable using combine command
for (i in 1:100){
  a<-c(a,i) # keeps combining a with itself and the new number in i
}
print(a)

# seq solution
a <- seq(1,100,1) # look up help for seq using ?seq() in console
print(a)

```

# Replace this with problem 4

And keep going. Try to solve the problems with different scripts that provide the same solution. Good luck, Happy coding.
